---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# youtubeFunction

<!-- badges: start -->
![](https://github.com/DSCI-310/dsci-310-group-13-pkg/actions/workflows/test-coverage.yaml/badge.svg)
[![codecov](https://codecov.io/gh/DSCI-310/dsci-310-group-13-pkg/branch/main/graph/badge.svg?token=akuR6bS6ic)](https://codecov.io/gh/DSCI-310/dsci-310-group-13-pkg)


<!-- badges: end -->

# youtubeFunction (1.0.0)


The goal of youtubeFunction is to build functions that are used for DSCI-310 group 13 term project instead of using repetitive lines of codes. The functions in this package are built on functions in other packages, such as tidyverse, dplyr, parsnip, workflows, etc. These functions have similar abilities as their built-on functions; however, they have more specific functionalities, such as: reading specific data from the container we built, cleaning the data in a specific way, and fitting the model in a specific workflow. Therefore, this package may not be practical other than in this project.  

If you are interested at reading the **vignettes** for this package on *a pkgdown site*, you can click [here](https://dsci-310.github.io/dsci-310-group-13-pkg/articles/Intro_to_youtubeFunction.html). The vignettes are very similar to the Usage section below, but with a little bit more details on how the functions are used in the container. 


### Functions included:
- `read_raw_data()`
- `bind_tables()`
- `read_uncleaned_data()`
- `wrangling_data()`
- `fit_regression()`


## Installation

You can install the development version of youtubeFunction from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("DSCI-310/dsci-310-group-13-pkg")
```

## Usage
\

### read_raw_data()

The function read_raw_data() read the URL of specific data sets from our project repository on [Github](https://github.com/DSCI-310/dsci-310-group-13) or an absolute path to the data files stored in our Docker container:
```{r raw,warning=FALSE, message=FALSE}
library(youtubeFunction)
## This example reads the raw data sets for 2007 YouTube data
table0007 <- read_raw_data("https://raw.githubusercontent.com/DSCI-310/dsci-310-group-13/main/data/0007.txt")
table0107 <- read_raw_data("https://raw.githubusercontent.com/DSCI-310/dsci-310-group-13/main/data/0107.txt")
table0207 <- read_raw_data("https://raw.githubusercontent.com/DSCI-310/dsci-310-group-13/main/data/0207.txt")
table0307 <- read_raw_data("https://raw.githubusercontent.com/DSCI-310/dsci-310-group-13/main/data/0307.txt")
```

\

### bind_tables()

The function bind_tables() takes in four tables that contains Youtube data for one year, binds them into one table, and omit the rows with NA:

```{r bind,warning=FALSE, message=FALSE}
library(youtubeFunction)
## This examples binds tables that contains YouTube data for 2007 into one table 
data2007_uncleaned <- bind_tables(table0007,table0107,table0207, table0307)

## change the column names of the dataset to meaningful ones
youtube_col_names <- c("Video ID", "uploader", "age", 'category','length',
                       'views','rate','ratings','comments','related IDs')
colnames(data2007_uncleaned) <- youtube_col_names

## show the first five rows of the raw data for 2007 with changed column names
head(data2007_uncleaned)
```

\

### read_uncleaned_data()

The function read_uncleaned_data() takes in an absolute path to read a saved out uncleaned data set from load.R, which reads in the raw data tables, combines those tables based on the year the data belongs to, and write out as txt files in the container, for example:

```{r uncleaned,warning=FALSE, message=FALSE}
## This is an example of how read_uncleaned_data() is used in the container
## where "/home/rstudio/data/" is the path to where the uncleaned data is saved in the container

## data2007_uncleaned <- youtubeFunction::read_uncleaned_data("/home/rstudio/data/data2007_not_cleaned.txt")
```

\

### wrangling_data()

The function wrangling_data() takes in an uncleaned youtube data set and tidies it so that the data set only contains "age", "category", "length", "views", "rate", "ratings", "comments" as columns. For instance:

```{r wrangling,warning=FALSE, message=FALSE}
## This is an example of using wrangling_data() to tidy up the 
## uncleaned YouTube data for 2007
data2007 <- youtubeFunction::wrangling_data(data2007_uncleaned)
head(data2007)
```

\

### fit_regression()

The following R chunk prepossesses the data set and splits the data into train data and test data, where the train data is used to fit the model used for our prediction.

```{r, split,warning=FALSE, message=FALSE}
datareduced <- data2007 |>  dplyr::select(c(views,age,ratings,comments))
split <- rsample::initial_split(datareduced, prop = 3/4, strata = views)
train <- rsample::training(split)
test <- rsample::testing(split)
```


The function fit_regression() takes in the training data and fits a simple linear regression to chosen columns with the response variable `views`.
```{r, fit_regression,warning=FALSE, message=FALSE}
lm_fit <- fit_regression(train)
lm_fit 
```

