---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# youtubeFunction

<!-- badges: start -->
![](https://github.com/chris-ckh/dsci-310-group-13-pkg/actions/workflows/test-coverage.yaml/badge.svg)
<!-- badges: end -->

The goal of youtubeFunction is to build functions that are used for DSCI-310 group 13 term project. This package includes functions that read raw data, read unclenaed data, clean the data, bind tables, and fit the model. 

## Installation

You can install the development version of youtubeFunction from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chris-ckh/dsci-310-group-13-pkg")
```

## Usage

The function read_raw_data() takes in an URL to one of raw data sets in the data folder from our Github page :

```{r raw}
library(youtubeFunction)
## table0007 <- read_raw_data("https://raw.githubusercontent.com/chris-ckh/dsci-310-group-13/main/data/0007.txt")
```

The function bind_tables() takes in four tables that contains Youtube data for one year, and binds them into one table:

```{r bind}
library(youtubeFunction)
## This examples binds tables that contains YouTube data for 2007 into one table 
## data2007_uncleaned <- bind_tables(table0007,table0107,table0207, table0307)
```

The function read_uncleaned_data() takes in an path to read a saved out uncleaned data set from load.R, for example:

```{r uncleaned}
## "/home/rstudio/data/" is the path to where the uncleaned data is saved
## data2007_uncleaned <- read_uncleaned_data("/home/rstudio/data/data2007_not_cleaned.txt")
```

The function wrangling_data() takes in an uncleaned youtube data set and tidies it so that the data set only contains "age", 'category', 'length','views','rate','ratings','comments' as columns. For instance:
```{r wrangling}
## "/home/rstudio/data/" is the path to where the uncleaned data is saved
## data2007 <- wrangling_data(data2007_uncleaned)
```

The function fit_regression() takes in the training data and fits a simple linear regression to said data with the response variable `views`.
```{r, fit_regression}
## lm <- fit_regression(training)
```

