---
title: "Introduction to youtubeFunction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to youtubeFunction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Functions included for this package:
- `read_raw_data()`
- `bind_tables()`
- `read_uncleaned_data()`
- `wrangling_data()`
- `fit_regression()`

```{r setup}
library(youtubeFunction)
```

### read_raw_data( )
This function reads the URL of specific data sets from our project repository on [Github](https://github.com/DSCI-310/dsci-310-group-13) or an absolute path to the data files stored in our Docker container:

\
#### example for reading raw data sets for 2007 YouTube data from our project repository
```{r raw,warning=FALSE, message=FALSE}
## This example reads the raw data sets for 2007 YouTube data
## saved on our Github repository
table0007 <- read_raw_data("https://raw.githubusercontent.com/DSCI-310/dsci-310-group-13/main/data/0007.txt")
table0107 <- read_raw_data("https://raw.githubusercontent.com/DSCI-310/dsci-310-group-13/main/data/0107.txt")
table0207 <- read_raw_data("https://raw.githubusercontent.com/DSCI-310/dsci-310-group-13/main/data/0207.txt")
table0307 <- read_raw_data("https://raw.githubusercontent.com/DSCI-310/dsci-310-group-13/main/data/0307.txt")
```

\
#### example for reading raw data sets for 2007 YouTube data in the Docker container
```{r rawDocker,warning=FALSE, message=FALSE}
## "/home/rstudio/data/" is the absolute path for the data folder
## in our container

## table0007 <- read_raw_data("/home/rstudio/data/0007.txt")
## table0107 <- read_raw_data("/home/rstudio/data/0107.txt")
## table0207 <- read_raw_data("/home/rstudio/data/0207.txt")
## table0307 <- read_raw_data("/home/rstudio/data/0307.txt")
```

### bind_tables( )
This function takes in four tables that contains Youtube data for one year, binds them into one table, and omit the rows with NA:
```{r bind,warning=FALSE, message=FALSE}
library(youtubeFunction)
## This examples binds tables that contains YouTube data for 2007 into one table 
data2007_uncleaned <- bind_tables(table0007,table0107,table0207, table0307)

## change the column names of the dataset to meaningful ones
youtube_col_names <- c("Video ID", "uploader", "age", 'category','length',
                       'views','rate','ratings','comments','related IDs')
colnames(data2007_uncleaned) <- youtube_col_names

## show the first five rows of the raw data for 2007 with changed column names
head(data2007_uncleaned)
```

### read_uncleaned_data( )

This function takes in an absolute path to read a saved out uncleaned data set from load.R, which reads in the raw data tables, combines those tables based on the year the data belongs to, and write out as txt files in the container, for example:

```{r uncleaned,warning=FALSE, message=FALSE}
## This is an example of how read_uncleaned_data() is used in the container
## where "/home/rstudio/data/" is the path to where the uncleaned data is saved in the container

## data2007_uncleaned <- youtubeFunction::read_uncleaned_data("/home/rstudio/data/data2007_not_cleaned.txt")
```

### wrangling_data( )

This function takes in an uncleaned youtube data set and tidies it so that the data set only contains "age", "category", "length", "views", "rate", "ratings", "comments" as columns. For instance:

```{r wrangling,warning=FALSE, message=FALSE}
## This is an example of using wrangling_data() to tidy up the 
## uncleaned YouTube data for 2007
data2007 <- youtubeFunction::wrangling_data(data2007_uncleaned)
head(data2007)
```

### fit_regression( )

The following R chunk prepossesses the data set and splits the data into train data and test data, where the train data is used to fit the model used for our prediction.

```{r, split,warning=FALSE, message=FALSE}
datareduced <- data2007 |>  select(c(views,age,ratings,comments))
split <- rsample::initial_split(datareduced, prop = 3/4, strata = views)
train <- rsample::training(split)
test <- rsample::testing(split)
```


The function fit_regression() takes in the training data and fits a simple linear regression to chosen columns with the response variable `views`.
```{r, fit_regression,warning=FALSE, message=FALSE}
lm_fit <- fit_regression(train)
lm_fit 
```
